---
title: "Writing Functions"
output: github_document

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
library(dplyr)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Do something simple

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)
(x_vec - mean(x_vec)) / sd(x_vec)
```
```


I want a function to compute z-scores
```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
 
 return(z)
  
}

z_scores(x_vec)
```

Try my function on some other things

```{r}
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
    
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
    }
    
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}
```



## Multiple outputs

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)
(x_vec - mean(x_vec)) / sd(x_vec)
```
```


I want a function to compute z-scores
```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
 
 return(z)
  
}

z_scores(x_vec)
```

Try my function on some other things

```{r}
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
    
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
    }
    
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
 mean_x = mean(x)
 sd_x = sd(x)
  
tibble(
  mean = mean_x,
  sd = sd_x
)

}
```

Check that the function works.
```{r}
x_vec = rnorm(100, mean = 3, sd = 4)
mean_and_sd(x_vec)
```

## multiple inputs

```{r}
sim_data = 
tibble(
x = rnorm(100, mean = 4, sd = 3)
)

sim_data %>% 
summarize(
mean = mean(x),
sd = sd(x)
)
```


```{r}
sim_mean_sd = function(samp_size, mu = 3, sigma = 4) {

sim_data = 
tibble(
x = rnorm(n = samp_size, mean = 4, sd = 3)
)

sim_data %>% 
summarize(
mean = mean(x),
sd = sd(x)
)

}

sim_mean_sd(samp_size = 100, mu = 6, sigma = 3)
```

## Let's review Napoleon Dynamite
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```


A function that will allow us to scrape data from any Amazon review page via URL
```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

Reading in reviews from several pages and combining results
```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

dynamite_reviews
```


## Mean scoping example
```{r}
f = function(x) {
z = x + y
z
}

x = 1
y = 2

f(x = y)
```


Functions as arguments
```{r}
x_vec = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}

my_summary(x_vec, sd)
```

